\section{Work Experience}
\begin{center}

\begin{atomtable}
	Present & .NET Developer \\
	Sept. 2018 & Egara Optiminn\\
	~		& I am currently working as a .NET developer at Egara Optiminn.
	
	Egara Optiminn aims to provide efficient and modern solutions for banking entities regarding documentation processing.\\
\end{atomtable}

\vspace{5mm}
	
\begin{atomtable}
	Sept. 2018 & Java Developer \\
	June 2018 & E-TIC Sistemes \\
	~		& I worked as a junior developer for e-tic sistemas at Grupo Godó.

My responsibilities here are working on the editorial software Mundo Deportivo's writers are using, based on Java7.\\
\end{atomtable}

\vspace{5mm}

\begin{atomtable}
	Feb 2018	& Unity3D Teacher \\
	& Video Games Association of the FIB \\
	~		& Teacher at a course about advanced topics for Unity. Several subjects were taught, including shader development, serialization, optimisation, game design, multiplatform development, etc. \\
\end{atomtable}

\vspace{5mm}

\begin{atomtable}
	Sept 2017	& .NET Developer \\
	June 2017	& Tiendeo \\
	~		& Summer internship at Tiendeo, worked with some great people and learned a lot through the process. My work there was mainly about backend/backoffice challenges in C\#. \\
\end{atomtable}

\vspace{5mm}

\begin{atomtable}
	Sept 2016	& Visual Basic Developer 	\\
	Aug 2016	& IRTA \\
	~		& Internsip at the Institute of Research and Agrifood Technologies. My work there consisted on programming a series of Excel macros using Visual Basic.\\
\end{atomtable}

\vspace{5mm}

\begin{atomtable}
	Sept 2014	& Product Designer 	\\
	Jun 2013	& Feeling Projects 	\\
	~		& Work done at a startup in my hometown, Lleida. I helped with the design of various projects we were working on at the moment. Great experience. \\
\end{atomtable}

\end{center}
